\ZpL: a p-adic precision package

### 2018-01-30 ZpL/ZpL.tex
Small improvement in one tikz picture
Most examples done

\usepackage{amsmath,amssymb}
%\usepackage{amsthmnoproof}
\usepackage{amsthm}
\usepackage{mathrsfs}
%\let\bibsection\relax
%\usepackage{amsrefs}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{stmaryrd}
\usepackage{enumerate}
%\usepackage[algoruled,vlined,english,linesnumbered]{algorithm2e}
%\usepackage[pdfpagelabels,colorlinks=true,citecolor=blue]{hyperref}
\usepackage{comment}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{tabularx,multicol}
\usepackage{tikz}

@@

\newcommand{\sage}{\textsc{SageMath}\xspace}
\newcommand{\ZpL}{\text{\rm \tt ZpL}\xspace}
\newcommand{\ZpLC}{\text{\rm \tt ZpLC}\xspace}
\newcommand{\ZpLF}{\text{\rm \tt ZpLF}\xspace}

@@

\begin{tabular}{|l|l|}
\verb?R = Zp(3,5)? & \verb?R = ZpL(3,5)? \\
\verb?x = R(143,5); x? & \verb?x = R(143,5); x? \\
\hfill\verb?...12022? & \hfill\verb?...12022? \\
\verb?3*x? & \verb?3*x? \\
\hfill\verb?...120220? & \hfill\verb?...120220? \\
\verb?x + x + x? & \verb?x + x + x? \\
\hfill\verb?...20220? & \hfill\verb?...120220? \\
\verb?x^3? & \verb?x^3? \\
\hfill\verb?...020222? & \hfill\verb?...020222? \\
\verb?x * x * x? & \verb?x * x * x? \\
\hfill\verb?...20222? & \hfill\verb?...020222? \\
\end{tabular}

\begin{tabular}{|l|l|}
\verb?R = Zp(2,10)? & \verb?R = ZpL(2,10)? \\
\verb?x = R(987,10); x? & \verb?x = R(987,10); x? \\
\hfill\verb?...1111011011? & \hfill\verb?...1111011011? \\
\verb?y = R(21,5); y? & \verb?y = R(21,5); y? \\
\hfill\verb?...10101? & \hfill\verb?...10101? \\
\verb?u = x + y; u? & \verb?u = x + y; u? \\
\hfill\verb?...10000? & \hfill\verb?...10000? \\
\verb?v = x - y; v? & \verb?v = x - y; v? \\
\hfill\verb?...00110? & \hfill\verb?...00110? \\
\verb?u + v? & \verb?u + v? \\
\hfill\verb?...10110? & \hfill\verb?...11110110110? \\
\end{tabular}

@@

\bigskip

@@

More precisely, in the \ZpLC case, the obtained matrix has this 
shape:
$$\left(\raisebox{-0.5\height}{\begin{tikzpicture}[scale=0.3]
\fill[black!20] (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-4)--(4,-4)--(4,-5)--(5,-5)--(5,-6)--(6,-6)
    --(6,-7)--(7,-7)--(7,0)--cycle;
\draw (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-4)--(4,-4)--(4,-5)--(5,-5)--(5,-6)--(6,-6)
    --(6,-7)--(7,-7);
\draw[thin] (7,-7)--(7,0)--(0,0);
\fill (3,0) rectangle (4,-4);
\draw[->] (2.9,-4.8)--(3.2,-4.2);
\node[scale=0.8] at (2,-5.2) { deleted };
\node[scale=0.8] at (2,-6) { column };
\end{tikzpicture}}\right)
\quad = \quad
\left(\raisebox{-0.5\height}{\begin{tikzpicture}[scale=0.3]
\fill[black!20] (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-5)--(4,-5)--(4,-6)--(5,-6)--(5,-7)--(6,-7)--(6,0)--cycle;
\draw (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-5)--(4,-5)--(4,-6)--(5,-6)--(5,-7)--(6,-7);
\draw[thin] (6,-7)--(6,0)--(0,0);
\end{tikzpicture}}\right)$$
where a cell is colored when it can contain a non-vanishing entry.
The top part of the matrix is then already echenolized, so that we
only have to re-echelonize the bottom right corner whose size is
the distance from the column corresponding to the erased variable
to the end. 
Thanks to the particular shape of the matrix, the echelonization can be 
performed efficiently: we combine the first rows (of the bottom right 
part) in order to clear the first unwanted nonzero entry and then 
proceed recursively.

@@

\begin{tabular}{|l|l|}
\verb?R = Zp(2)? & \verb?R = ZpL(2)? \\
\multicolumn{2}{|l|}{\tt x, y, z, t = R(1,15), R(1,15), R(1,15), R(3,15)} \\
\multicolumn{2}{|l|}{\tt for \_ in range(20):} \\
\multicolumn{2}{|l|}{\tt \ \ \ \ x, y, z, t = y, z, t, (y*t + z*z)/x} \\
\multicolumn{2}{|l|}{\tt \ \ \ \ print t} \\
\hfill\verb?...000000000000100? & \hfill\verb?...000000000000100? \\
\hfill\verb?...000000000001101? & \hfill\verb?...000000000001101? \\
\hfill\verb?...000000000110111? & \hfill\verb?...000000000110111? \\
\hfill\verb?...101010111010111? & \hfill\verb?...101010111010111? \\
\hfill\verb?...1100111101111? & \hfill\verb?...101100111101111? \\
\hfill\verb?...1110000010010? & \hfill\verb?...111110000010010? \\
\hfill\verb?...0001000111001? & \hfill\verb?...100001000111001? \\
\hfill\verb?...0000011111101? & \hfill\verb?...100000011111101? \\
\hfill\verb?...1000000110101? & \hfill\verb?...001000000110101? \\
\hfill\verb?...101101010011? & \hfill\verb?...010101101010011? \\
\hfill\verb?...110000000000? & \hfill\verb?...001110000000000? \\
\hfill\verb?...000101011101? & \hfill\verb?...111000101011101? \\
\hfill\verb?...001001101011? & \hfill\verb?...111001001101011? \\
\hfill\verb?...000011110011? & \hfill\verb?...111000011110011? \\
\hfill\verb?...11? & \hfill\verb?...0000000111? \\
\hfill\verb?...10? & \hfill\verb?...1010001110? \\
\hfill\verb?...01? & \hfill\verb?...1110110001? \\
\hfill\verb?...01? & \hfill\verb?...011110111001? \\
\hfill\verb?...01? & \hfill\verb?...100101101001001? \\
\hfill\verb?...1? & \hfill\verb?...11111000011? \\
\end{tabular}

\begin{itemize}
\item SOMOS sequence
\item many multiplications of matrices
\item Dodgson algorithm
\item subresultants
\item Grobner basis
\item $p$-adic differential equations
\end{itemize}

@@

\begin{tabular}{rl}
\cIn
 & \verb?Q2 = Qp(2, prec=50, print_mode="digits")? \\
 & \verb?R.<x,y,z> = PolynomialRing(Q2, order = 'invlex')? \\
 & \verb?F = [Q2(2,10)*x + Q2(1,10)*z, ? \\
 & \verb?     Q2(1,10)*x^2 + Q2(1,10)*y^2 - Q2(2,10)*z^2,? \\
 & \verb?     Q2(4,10)*y^2 + Q2(1,10)*y*z + Q2(8,10)*z^2]? \\
 & \verb?from sage.rings.polynomial.toy_buchberger?\\
 &\verb?  import buchberger_improved? \\
 & \verb?g = buchberger_improved(ideal(F)); g.sort()? \\
 & \verb?g? \\
\cZpCR
 & \verb?[x^3, x*y + ...1100010*x^2, y^2 + ...11001*x^2,? \\
 & \verb? z + ...0000000010*x]? \\
\cZpLC
 & \verb?[[x^3, x*y + ...111100010*x^2, y^2 + ...1111111001*x^2,? \\
 & \verb? z + ...0000000010*x]]? \\
\end{tabular}

As we can see, some loss in precision occurs in the
Buchberger algorithm.
Had we used \cZpFP , many padded zeroes or one would have appeared.

@@

\begin{tabular}{|l|l|}
\verb?R = Qp(2,250)? & \verb?R = QpL(2,250)? \\
\verb?S = Zp(2,250)? & \verb?S = ZpL(2,250)? \\
\multicolumn{2}{|l|}{\tt A.<x> = PowerSeriesRing(R,32) } \\
\multicolumn{2}{|l|}{\tt B.<x> = PowerSeriesRing(S,32)) } \\
\multicolumn{2}{|l|}{\tt h,y =1+x+x\^{}3 , x+x\^{}2*A(B.random\_element()) } \\
\multicolumn{2}{|l|}{\tt g=y.derivative()/h(y) } \\
\multicolumn{2}{|l|}{\tt s=Newton\_Iteration\_Solver(g,h,5)} \\
\multicolumn{2}{|l|}{\tt print 250-(s[31].lift()-y[31].lift()).valuation(2)} \\
\hfill\verb?9? & \hfill\verb?4? \\
\end{tabular}
The last line provides the loss in precision between the
original solution of the differential equation and its approximation
obtained through computation.
The theorical loss in precision for the coefficient of $t^{31}$
is $\lfloor log_2 (31)\rfloor=4$ and is then reached, whereas the
loss in precision for a naive implementation is clearly more severe.

@@

We can solve numerically 
the corresponding differential equation
using the algorithm of \cite{Lercier-Sirvent:08}
over $\mathbb{Q}_3$ with lattice precision.
We use an initial precision of 50 digits.
Any generic implementation of the Newton
method of \cite{Lercier-Sirvent:08} is enough.

\begin{tabular}{|l|}
\verb?    R = QpL(3,50)? \\
\verb?    A.<x> = PolynomialRing(R)?\\
\verb?    m=67?\\
\verb?    g=1+(1/4)*x^2+x^6?\\
\verb?    h=1+((m^2)/4)*x^2+m^6* x^6?\\
\verb?    y=Lercier_Sirvent(g,h,64)?\\
\verb?    y[31]?\\
\verb?(467995903278061284942799/3^14 + O(3^36))*x^31?\\
\end{tabular}

We can then see that up to $63,$ the behaviour
of the loss in relative precision is the same
as for the coefficient in $x^{31}$: \textbf{no loss
occured}.
Thus, those simple manipulations
hint at a different behaviour for the loss 
in precision in at least some special cases of
of isogenies defined over $\mathbb{Q}$
but not necessarily over $\mathbb{Z}_p.$

>>>>

\usepackage{amsmath,amssymb}
%\usepackage{amsthmnoproof}
\usepackage{amsthm}
\usepackage{mathrsfs}
%\let\bibsection\relax
%\usepackage{amsrefs}
%\usepackage[usenames,dvipsnames]{color}
\usepackage{stmaryrd}
\usepackage{enumerate}
%\usepackage[algoruled,vlined,english,linesnumbered]{algorithm2e}
%\usepackage[pdfpagelabels,colorlinks=true,citecolor=blue]{hyperref}
\usepackage{comment}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{tabularx,multicol}
\usepackage{tikz}
\usetikzlibrary{patterns}

@@

\newcommand{\sage}{\textsc{SageMath}\xspace}
\newcommand{\ZpCR}{\text{\rm \tt ZpCR}\xspace}
\newcommand{\ZpFP}{\text{\rm \tt ZpFP}\xspace}
\newcommand{\ZpL}{\text{\rm \tt ZpL}\xspace}
\newcommand{\ZpLC}{\text{\rm \tt ZpLC}\xspace}
\newcommand{\ZpLF}{\text{\rm \tt ZpLF}\xspace}

@@

We begin our tour of the features of the \ZpL package
with some basic arithmetic computations.
The first step is the definition of the $p$-adic ring or field.
\begin{tabular}{rl}
\cIn
 & \verb?Z3 = Zp(3, prec=20, print_mode="digits")? \\
\end{tabular}
It means that we will work in various implementation of the 
ring of $3$-adic integers with $20$ digits
of precision. 
We show the results for \ZpCR, \ZpFP and \ZpLC.
Results for \ZpLF are only shown when they differ from \ZpLC.
We first take some random element $x$.
\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z3,5)? \\
 & \verb?x? \\
\cZpCR
 & \verb?...11111? \\
\cZpFP
 & \verb?...00000000000000011111? \\
\cZpLC
 & \verb?...11111? \\
\end{tabular}
Multiplication by $3$ is a shift on the digits, whether it 
is done by addition or multiplication.

\begin{tabular}{rl}
\cIn
 & \verb?3*x? \\
\cZpCR
 & \verb?...111110? \\
\cZpFP
 & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\cIn
 & \verb?x + x + x? \\
\cZpCR
 & \verb?...11110? \\
\cZpFP
 & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}

Something is lost however in \ZpCR when performing
$x+2x.$

\begin{tabular}{rl}
\cIn
 & \verb?y = 2*x? \\
 & \verb?y? \\
\cZpCR
 & \verb?...22222? \\
\cZpFP
 & \verb?...00000000000000022222? \\
\cZpLC
 & \verb?...22222? \\
\cIn
 & \verb?x + y? \\
\cZpCR
 & \verb?...11110? \\
\cZpFP
 & \verb?...000000000000000111110? \\
\cZpLC
 & \verb?...111110? \\
\end{tabular}

The same phenomenon occurs when comparing the computation
of $x^3$ and $x \times x^2.$

\begin{tabular}{rl}
\cIn
 & \verb?x^3? \\
\cZpCR
 & \verb?...010101? \\
\cZpFP
 & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\
\cIn
 & \verb?y = x^2? \\
 & \verb?x * y? \\
\cZpCR
 & \verb?...10101? \\
\cZpFP
 & \verb?...00000010100000010101? \\
\cZpLC
 & \verb?...010101? \\

\end{tabular}

\ZpL is also well suited for working with coefficients 
with unbalanced precision.

\begin{tabular}{rl}
\cIn
 & \verb?x = random_element(Z2,10)? \\
 & \verb?y = random_element(Z2,5)? \\
\cIn
 & \verb?u = x+y? \\
 & \verb?u? \\
\cZpCR
 & \verb?...10111? \\
\cZpFP
 & \verb?...000000000000000000000011010111? \\
\cZpLC
 & \verb?...10111? \\
\cIn
 & \verb?v = x-y? \\
 & \verb?v? \\
\cZpCR
 & \verb?...01111? \\
\cZpFP
 & \verb?...000000000000000000000011001111? \\
\cZpLC
 & \verb?...01111? \\
\end{tabular}

Now, let us compute $u+v=2 \times x.$

\begin{tabular}{rl}
\cIn
 & \verb?u+v? \\
\cZpCR
 & \verb?...00110? \\
\cZpFP
 & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\cIn
 & \verb?2*x? \\
\cZpCR
 & \verb?...00110100110? \\
\cZpFP
 & \verb?...0000000000000000000000110100110? \\
\cZpLC
 & \verb?...00110100110? \\
\end{tabular}

No loss in precision appears in \ZpLC, contrary to \ZpCR.
We remark that \ZpFP also provides all the correct digits.

@@

@@

More precisely, in the \ZpLC case, the obtained matrix has this 
shape:
$$\left(\raisebox{-0.5\height}{\begin{tikzpicture}[scale=0.3]
\fill[black!20] (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-4)--(4,-4)--(4,-5)--(5,-5)--(5,-6)--(6,-6)
    --(6,-7)--(7,-7)--(7,0)--cycle;
\draw (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-4)--(4,-4)--(4,-5)--(5,-5)--(5,-6)--(6,-6)
    --(6,-7)--(7,-7);
\draw[thin] (7,-7)--(7,0)--(0,0);
\begin{scope}
\clip (3,0.2) rectangle (4,-4.2);
\draw[pattern=north east lines] (2.5,0.5) rectangle (4.5,-4.5);
\end{scope}
\draw[->] (2.9,-4.8)--(3.2,-4.2);
\node[scale=0.8] at (2,-5.2) { deleted };
\node[scale=0.8] at (2,-6) { column };
\end{tikzpicture}}\right)
\quad = \quad
\left(\raisebox{-0.5\height}{\begin{tikzpicture}[scale=0.3]
\fill[black!20] (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-5)--(4,-5)--(4,-6)--(5,-6)--(5,-7)--(6,-7)--(6,0)--cycle;
\draw (0,0)--(0,-1)--(1,-1)--(1,-2)--(2,-2)--(2,-3)
    --(3,-3)--(3,-5)--(4,-5)--(4,-6)--(5,-6)--(5,-7)--(6,-7);
\draw[thin] (6,-7)--(6,0)--(0,0);
\end{tikzpicture}}\right)$$
where a cell is colored when it can contain a non-vanishing entry.
The top part of the matrix is then already echenolized, so that we
only have to re-echelonize the bottom right corner whose size is
the distance from the column corresponding to the erased variable
to the end. 
Thanks to the particular shape of the matrix, the echelonization can be 
performed efficiently: we combine the first rows (of the bottom right 
part) in order to clear the first unwanted nonzero entry and then 
proceed recursively.

@@

\subsection{SOMOS-4}

The SOMOS-4 sequence is a well-known example
of a computation with a large gap between
the theoretical loss in precision
and that of a naive computation (see \cite{caruso-roe-vaccon:14a}).
We show here that precision can be saved
even when using a generic implementation
of the SOMOS iteration.

\begin{tabular}{rl}
\cIn
 & \verb?def somos4(u0, u1, u2, u3, n):? \\
 & \verb?    a, b, c, d = u0, u1, u2, u3? \\
 & \verb?    for _ in range(4, n+1):? \\
 & \verb?        a, b, c, d = b, c, d, (b*d + c*c) / a? \\
 & \verb?    return d? \\
\end{tabular}
\begin{tabular}{rl}
\cIn
 & \verb?somos4(Z2(1,15), Z2(1,15), Z2(1,15), Z2(3,15), 18)? \\
\cZpCR
 & \verb?...11? \\
\cZpFP
 & \verb?...110111001000100100000000000111? \\
\cZpLC
 & \verb?...100000000000111? \\
\cIn
 & \verb?somos4(Z2(1,15), Z2(1,15), Z2(1,15), Z2(3,15), 100)? \\
\cZpCR
 & \verb?PrecisionError: cannot divide by something?\\
 &\verb?indistinguishable from zero.? \\
\cZpFP
 & \verb?...110000101000011001001001110001? \\
\cZpLC
 & \verb?...001001001110001? \\
\end{tabular}
%
%\begin{tabular}{|l|l|}
%\verb?R = Zp(2)? & \verb?R = ZpL(2)? \\
%\multicolumn{2}{|l|}{\tt x, y, z, t = R(1,15), R(1,15), R(1,15), R(3,15)} \\
%\multicolumn{2}{|l|}{\tt for \_ in range(20):} \\
%\multicolumn{2}{|l|}{\tt \ \ \ \ x, y, z, t = y, z, t, (y*t + z*z)/x} \\
%\multicolumn{2}{|l|}{\tt \ \ \ \ print t} \\
%\hfill\verb?...000000000000100? & \hfill\verb?...000000000000100? \\
%\hfill\verb?...000000000001101? & \hfill\verb?...000000000001101? \\
%\hfill\verb?...000000000110111? & \hfill\verb?...000000000110111? \\
%\hfill\verb?...101010111010111? & \hfill\verb?...101010111010111? \\
%\hfill\verb?...1100111101111? & \hfill\verb?...101100111101111? \\
%\hfill\verb?...1110000010010? & \hfill\verb?...111110000010010? \\
%\hfill\verb?...0001000111001? & \hfill\verb?...100001000111001? \\
%\hfill\verb?...0000011111101? & \hfill\verb?...100000011111101? \\
%\hfill\verb?...1000000110101? & \hfill\verb?...001000000110101? \\
%\hfill\verb?...101101010011? & \hfill\verb?...010101101010011? \\
%\hfill\verb?...110000000000? & \hfill\verb?...001110000000000? \\
%\hfill\verb?...000101011101? & \hfill\verb?...111000101011101? \\
%\hfill\verb?...001001101011? & \hfill\verb?...111001001101011? \\
%\hfill\verb?...000011110011? & \hfill\verb?...111000011110011? \\
%\hfill\verb?...11? & \hfill\verb?...0000000111? \\
%\hfill\verb?...10? & \hfill\verb?...1010001110? \\
%\hfill\verb?...01? & \hfill\verb?...1110110001? \\
%\hfill\verb?...01? & \hfill\verb?...011110111001? \\
%\hfill\verb?...01? & \hfill\verb?...100101101001001? \\
%\hfill\verb?...1? & \hfill\verb?...11111000011? \\
%\end{tabular}
%
%\begin{itemize}
%\item SOMOS sequence
%\item many multiplications of matrices
%\item Dodgson algorithm
%\item subresultants
%\item Grobner basis
%\item $p$-adic differential equations
%\end{itemize}

\subsection{Matrix multiplication}
The multiplication of many matrices has been studied
in \citep{caruso-roe-vaccon:15} and is known to often 
provide an heavy diffused digits phenomenon.
Here is a sample example. the result for \ZpFP has not been
added, but its first digits coincide with that of \ZpLC.

\begin{tabular}{rl}
\cIn
 & \verb?Z2 = Zp(2, prec=100)? \\
 & \verb?MS2 = MatrixSpace(Z2,2,2)? \\
 & \verb?Mat = random_element(MS2,prec=5)? \\
 & \verb?for _ in range(100):? \\
 & \verb?    Mat = Mat*random_element(MS2, prec=5)? \\
 & \verb?Mat? \\
\cZpCR
 & \verb?[ O(2^9) O(2^11)]? \\
 & \verb?[ O(2^9) O(2^11)]? \\
\cZpLC
 & \verb?[2^9 + 2^10 + 2^11 + O(2^12)  O(2^14)]? \\
 & \verb?[       2^9 + 2^11 + O(2^12)  O(2^14)]? \\
\end{tabular}

\ZpL can count the number of diffusede digits.

\begin{tabular}{rl}
\cIn
 & \verb?Z2.precision().number_of_diffused_digits()? \\
\cZpLC
 & \verb?604? \\
\end{tabular}

@@

\begin{tabular}{rl}
\cIn
 & \verb?Q2 = Qp(2, prec=50, print_mode="digits")? \\
 & \verb?R.<x,y,z> = PolynomialRing(Q2, order = 'invlex')? \\
 & \verb?F = [Q2(2,10)*x + Q2(1,10)*z, ? \\
 & \verb?     Q2(1,10)*x^2 + Q2(1,10)*y^2 - Q2(2,10)*z^2,? \\
 & \verb?     Q2(4,10)*y^2 + Q2(1,10)*y*z + Q2(8,10)*z^2]? \\
 & \verb?from sage.rings.polynomial.toy_buchberger?\\
 &\verb?  import buchberger_improved? \\
 & \verb?g = buchberger_improved(ideal(F)); g.sort()? \\
 & \verb?g? \\
\cZpCR
 & \verb?[x^3, x*y + ...1100010*x^2, y^2 + ...11001*x^2,? \\
 & \verb? z + ...0000000010*x]? \\
\cZpLC
 & \verb?[[x^3, x*y + ...111100010*x^2,? \\
 & \verb?y^2 + ...1111111001*x^2, z + ...0000000010*x]]? \\
\end{tabular}

As we can see, some loss in precision occurs in the
Buchberger algorithm and is avoided thanks to \ZpL.
Had we used \cZpFP , many padded zeroes or one would have appeared.

@@

\begin{tabular}{rl}
\cIn
 & \verb?N = 4? \\
 & \verb?Z2 = Zp(2, prec=50, print_mode="digits")? \\
 & \verb?Q2=Z2.fraction_field()? \\
 & \verb?S.<t> = PowerSeriesRing(Q2, 2^N)? \\
 & \verb?h = 1 + t + t^3? \\
 & \verb?y = t + t^2 * random_element(S,10)? \\
 & \verb?g = y.derivative() / h(y)? \\
 & \verb?u = Newton_Iteration_Solver(g, h, N)? \\
 & \verb?u[15]? \\
\cZpCR
 & \verb?...1101? \\
\cZpLC
 & \verb?...11011101? \\
\end{tabular}

%\begin{tabular}{|l|l|}
%\verb?R = Qp(2,250)? & \verb?R = QpL(2,250)? \\
%\verb?S = Zp(2,250)? & \verb?S = ZpL(2,250)? \\
%\multicolumn{2}{|l|}{\tt A.<x> = PowerSeriesRing(R,32) } \\
%\multicolumn{2}{|l|}{\tt B.<x> = PowerSeriesRing(S,32)) } \\
%\multicolumn{2}{|l|}{\tt h,y =1+x+x\^{}3 , x+x\^{}2*A(B.random\_element()) } \\
%\multicolumn{2}{|l|}{\tt g=y.derivative()/h(y) } \\
%\multicolumn{2}{|l|}{\tt s=Newton\_Iteration\_Solver(g,h,5)} \\
%\multicolumn{2}{|l|}{\tt print 250-(s[31].lift()-y[31].lift()).valuation(2)} \\
%\hfill\verb?9? & \hfill\verb?4? \\
%\end{tabular}
%The last line provides the loss in precision between the
%original solution of the differential equation and its approximation
%obtained through computation.
%The theorical loss in precision for the coefficient of $t^{31}$
%is $\lfloor log_2 (31)\rfloor=4$ and is then reached, whereas the
%loss in precision for a naive implementation is clearly more severe.

@@

We can solve numerically 
the corresponding differential equation
using the algorithm of \cite{Lercier-Sirvent:08}
over $\mathbb{Q}_3$ with lattice precision.
We use an initial precision of 50 digits
and some generic implementation of the Newton
method of \cite{Lercier-Sirvent:08}.

\begin{tabular}{rl}
\cIn
 & \verb?R = Qp(3,50)? \\
 & \verb?A.<x> = PolynomialRing(R)? \\
 & \verb?m=67? \\
 & \verb?g=1+(1/4)*x^2+x^6? \\
 & \verb?h=1+((m^2)/4)*x^2+m^6* x^6? \\
 & \verb?y=Lercier_Sirvent(g,h,6)? \\
 & \verb?y[31]? \\
 & \verb?u = Newton_Iteration_Solver(g, h, N)? \\
 & \verb?u[15]? \\
\cZpCR
 & \verb?(467995903278061284942799/3^14 + O(3^36))*x^31? \\
\cZpLC
 & \verb?(467995903278061284942799/3^14 + O(3^36))*x^31? \\
\end{tabular}

We can then see that up to $63,$ the behaviour
of the loss in relative precision is the same
as for the coefficient in $x^{31}$: \textbf{no loss
occured}. This happens for \ZpCR as for \ZpLC,
and thus, \ZpCR seems to attain the optimal precision.
consequently, those simple manipulations
hint at a different behaviour for the loss 
in precision in at least some special cases of
of isogenies defined over $\mathbb{Q}$
but not necessarily over $\mathbb{Z}_p.$
